Eliminating object prior-bias from sparse-projection tomographic reconstructions

### 2021-09-12 paper/changes.tex
changes in Fig.1, 2, dataset-intro, mnior changes

This is correct for the dataset show, and we accept this to be true.

  That said, the goal of our previous and curent work is to provide a
  technique that can improve upon a chosen baseline reconstruction
  when measurements are extremely sparse. One may choose any baseline
  reconstruction for pedagogical, historical, or ocmmercial reasons,
  and is there a way to improve?

>>>>

This is correct for the dataset shown, and we accept this to be true.

  That said, the goal of our previous and curent work is to provide a
  technique that can improve upon a chosen baseline reconstruction
  when measurements are extremely sparse. One may choose any baseline
  reconstruction for pedagogical, historical, or commercial reasons,
  and is there a way to improve?

### 2021-09-12 paper/post_tci.tex
changed super to superior
changes in Fig.1, 2, dataset-intro, mnior changes

 \subsection{Difficulties}
 When the number of views is significantly reduced (this paper), a
 regularization prior alone is not sufficient.  In such cases
 additional information (`object-prior') specific to the current
 object being scanned (called the `test' henceforth) is useful in
 further improving the reconstruction.  While this has been done in
 the context of dynamic CT-scans (discussed more in
 Section~\ref{sec:related}), in this paper we use a set $S$ of
 previous scans of the same object. This is relevant in a longitudinal
 context: the acquisition of sequential CT scans of the same subject
 in order to track time-evolving changes within the subject's
 interior.

@@

%-------------------------------Dataset----------------------------
\section{Datasets}
\label{sec:datasets}
In this section, we present details of the biological and medical
datasets created and used for this work. For the first two datasets
namely, Potato and Okra, the forward imaging model is available, and
hence all reconstructions were performed from raw measurements. For
the other two datasets namely, Sprouts and Liver, the forward imaging
model was not available to us (due to propriety concerns) and hence
only reconstructed volumes of real data were at hand; we therefore
generated measurements from these datasets assuming a circular
cone-beam imaging model for 3D and a parallel-beam imaging model for
2D.

@@

\subsection{Datasets with the forward model available}
\label{sec:potatoAndOkra}

@@

\textit{Remark:} The test slice (unlike the Okra below) was designed
to show the presence of a new feature (last picture in
Fig.~\ref{fig:potato_dataset}. Although the potato is visually bland,
paradoxically, this becomes the reason that the Potato is challenging
if a new method has to be shown to be effective.  Simpler methods may
suffice.  Nevertheless, we show super performance with our method by
vastly reducing the number of measurements corresponding to the ground truth.

@@

\subsection{Datasets without the forward model}
These consist of longitudinal scans of a portion of a liver obtained
from Tata Memorial Centre (TMC) ~\cite{tmh} in Parel, Mumbai, and
longitudinal scans of Sprouts obtained from Australian National
University.

@@

\subsection{Reconstruction of datasets with forward model available}
\subsubsection{\textbf{Potato}}
\label{Sec:potato_spatially_varying}

@@

\subsection{Reconstruction of datasets without forward model}
\subsubsection{\textbf{Liver:}}
\label{sec:tmh}

>>>>

  When the number of views is significantly reduced (this paper), a
 regularization prior alone is not sufficient.  In such cases
 additional information (`object-prior') specific to the current
 object being scanned (called the `test' henceforth) is useful in
 further improving the reconstruction.  While this has been done in
 the context of dynamic CT-scans (discussed more in
 Section~\ref{sec:related}), in this paper we use a set $S$ of
 previous scans of the same object. This is relevant in a longitudinal
 context: the acquisition of sequential CT scans of the same subject
 in order to track time-evolving changes within the subject's
 interior. 
 \subsection{Difficulties}

@@

%-------------------------------Dataset----------------------------
\section{Datasets}
\label{sec:datasets}
In this section, we present details of the biological and medical
datasets created and used for this work. For the first two datasets
namely, Potato and Okra, the raw measurements and  corresponding
paramteres for cone-beam imaging model are available to us.
Hence all reconstructions on these datasets were performed directly
from real projection measurements. For the other two datasets namely, Sprouts and
Liver, the raw measurements and the parameters of imaging
model were not available to us (due to propriety concerns) and hence
only reconstructed volumes of real data were at hand; we therefore
generated measurements from these datasets assuming a circular
cone-beam imaging model for 3D and a parallel-beam imaging model for
2D.

@@

\subsection{Datasets with the imaging model available}
\label{sec:potatoAndOkra}

@@

\textit{Remark:} The test slice (unlike the Okra below) was designed
to show the presence of a new feature (last picture in
Fig.~\ref{fig:potato_dataset}. Although the potato is visually bland,
paradoxically, this becomes the reason that the Potato is challenging
if a new method has to be shown to be effective.  Simpler methods may
suffice.  Nevertheless, we show superior performance with our method by
vastly reducing the number of measurements corresponding to the ground truth.

@@

\subsection{Datasets without the imaging model}
These consist of longitudinal scans of a portion of a liver obtained
from Tata Memorial Centre (TMC) ~\cite{tmh} in Parel, Mumbai, and
longitudinal scans of Sprouts obtained from Australian National
University.

@@

\subsection{Reconstruction of datasets with imaging model available}
\subsubsection{\textbf{Potato}}
\label{Sec:potato_spatially_varying}

@@

\subsection{Reconstruction of datasets without imaging model}
\subsubsection{\textbf{Liver:}}
\label{sec:tmh}
